\begin{deluxetable*}{lccllcll}
\singlespace
\setlength{\tabcolsep}{0.0001in} 
\tablewidth{514.88pt}
\tablecaption{Discovery and Classification Data for SN Sample}
\tablehead{\colhead{SN Name}  & 
\colhead{CfA spectra\tablenotemark{a}}&
\colhead{CfA NIR\tablenotemark{b}}&
\colhead{RA}&
\colhead{Dec}& 
\colhead{SN Type\tablenotemark{c}}  &  
\colhead{Discovery Date}  &  
\colhead{Discovery Reference} } 
\startdata
\input{tables/Discoverydata}
\enddata
\tablenotetext{1}{Indicates SN whose early-time behavior have been studied in the literature. $^\mathrm{2}$ Included in the D11 sample. }
\tablenotetext{3}{Radio studies, no published optical lightcurve. $^4$Progenitor studies, no published lightcurve.$^5$Host studies, no published lightcurve.$^6$Only spectra published.$^7$Only UV data published.}    
\tablenotetext{a}{Object whose names are bold in the table have spectra presented in M14}
\tablenotetext{b}{Object for which NIR data is available within the CfA survey. $^\mathrm{*}$Indicates \emph{only} NIR data is available within the CfA survey for this object.}
\tablenotetext{c}{SN reclassified with SNID using updated templates in M14 have the new classification reported.} 
\tablenotetext{d}{SN~2005la is spectroscopically peculiar showing narrow He and H lines in emission (Pastorello 2008).}
\tablenotetext{e}{SN~2006jc is spectroscopically peculiar and  showed narrow He lines in emission. See text for details. }
\tablenotetext{f}{The type classification of SN 2009er remains ambiguous. SNID classifies SN 2009er differentlly at different epochs. We also note the presence of high velocity He I lines.}
\label{tab:sample}
\end{deluxetable*}
