\begin{turnpage}
\tabletypesize{\tiny}
\begin{deluxetable*}{llccclcr}
  \singlespace

\centering
\tablewidth{614.88pt}
\tablecaption{Data suitable for extraction of ejecta properties}
\tablehead{\\
\colhead{SN}  & 
\colhead{SN Type}  &
%\colhead{GRB} &
\colhead{optical \tablenotemark{a}}&
\colhead{NIR \tablenotemark{b}}&
\colhead{UV \tablenotemark{c}}&
\colhead{other\tablenotemark{d}}&
\colhead{spectra \tablenotemark{e}}&
\colhead{phase \tablenotemark{e}}}

\startdata
%\tabletypesize{\scriptsize}
\input{tables/ejectadata_refdata}
\enddata
\tablenotetext{a}{Reference for Optical lightcurve.}
\tablenotetext{b}{Reference for NIR lightcurve.}
\tablenotetext{c}{Reference for UV lightcurve.}
\tablenotetext{d}{Wheather X-ray or Radio observations are available.}
\tablenotetext{e}{Reference for Spectra and phase, with respect to \maxep, as calculated from the reference photometry following the prescription in B14.}
%\tablenotetext{e}{`Y': the photospheric velocity is measured from a single spectrum within 2 days of \maxep, `N': photospheric velocity is measured from two spectra stradling \maxep and within eight days of \maxep.}
\tablenotetext{2}{Photometry provided by Kevin Krisciunas.}
\tablenotetext{3}{This is synthetic photometry generated from early spectra, and it is used to determine \maxep in absence of observations in optical wavelengths before $V$-band maximum.}
\tablenotetext{4}{\maxep determined from $R$ band lightcurve.}
\tablenotetext{5}{The optical band photometry is collected by Swift in the $u,~b,~v$ photometric bands. The $v$ band is used to calculate \maxep, and the photometry is converted following the prescription ???}
\tablenotetext{6}{Optical data was downloaded from Wiserep at the URL \url{http://wiserep.weizmann.ac.il/sites/weizmann.ac.il.wiserep/files/uploads/Ascii/iPTF13bvn_LC.tbl}, UV data  is  digitized from a plot  of the  Swift data  at the  URL  \url{http://arohatgi.info/WebPlotDigitizer/app/?}  using Ankit Rohatgi's  
WebPlotDigitizer online tool at \url{http://arohatgi.info/WebPlotDigitizer/}}
\label{tab:fullsample}
\end{deluxetable*}
\end{turnpage}
